\section{General Mathematical Modelling of Disease Dynamics}
\label{chap:generalModeling}
In order to describe the dynamics of different infectious diseases two different approaches have been developed, which will be described in the following chapter.
The compartmental model usually divides the whole population into different groups (compartments) while the so called "agent-based" approach tries to model every single individual who could be affected by the respective illness. 
\subsection{Compartmental Modeling}
As mentioned above the compartments divide the whole population into several groups (compartments), which take different roles in the spreading of the studied disease.
The share $x_i$ on the total population of those groups with $x_i \in [0,1] \text{ and } \sum_i x_i =1 $ can in general be described as follows:
\begin{eqnarray}
&\text{     }\xrightarrow{\alpha_i}  x_i \xrightarrow{\lambda_{ij}}   \label{comp:general} \\
&{\nu_i} \downarrow  \nonumber
\end{eqnarray}
where $\alpha_i$ describes the influx to this group for example induced by births, $\lambda_{ij} x_i$ is the part of members of the group $x_i$ which becomes part of the group $x_j$ and $\nu_i x_i$ is the part of $x_i$ that stops being part of the system. A reason for that could be a dying individual. To simplify the notation in equation (\ref{comp:general}) the influx created by $\lambda_{ki} x_k$ to the compartment $x_i$ by another group $x_k$ has been included to the influx $\alpha_i$. If one includes the birth rate $\mu_i$, the term $\alpha_i$ becomes 
\begin{equation}
\alpha_i = \mu_i + \sum_{k\neq i}{}\lambda_{ki} x_k.
\end{equation}
Most of the time one will assume that the whole population is stable in size so that $\sum_i \mu_i = \sum_{k} \nu_k$. If the disease does not affect the mortality of the different states, one can assume $\mu_i = \alpha_i$.
Depending on the specific disease the compartments can vary, but most diseases fall in one of the following two example for compartmental models.
\subsubsection{SIR-Model}\label{chap:sirBasic}
Diseases like the measles, which usually infect a human being only once in their life, can be modeled using an SIR-Model (Susceptible-Infected-Recovered-Model). One uses three compartments of individuals who are susceptible $x_1 = S$, infected $x_2=I$ or recovered $x_3=R$. The whole system is usually depicted as 
\begin{eqnarray}
\xrightarrow{\mu} &S \xrightarrow{\lambda_\text{SI}} &I  \xrightarrow{\lambda_\text{IR}} R  \\
{\nu_\text{S}} & \downarrow \text{         }\nu_\text{I} &\downarrow \text{  } {\nu_\text{R}} \downarrow \nonumber
\end{eqnarray}
with the simplifications that all newly born individuals are susceptible and that members of all compartments die with the same rate as new individuals are born ($\nu_i = \mu_i = \mu\, \forall i$). Furthermore one can assume that the transition rates $\lambda_\text{SI}$ (infection of a susceptible) and $\lambda_\text{IR}$ (recovery of an infected) individual are constant for all points in time.
If a system can be described like this, the stable state can be derived by using the following time derivatives:
\begin{eqnarray}
\dot{S} =& \mu -\lambda_\text{SI} SI &-  \mu S  \label{eq:sdotSIR}\\ 
\dot{I} =& \lambda_\text{SI} SI - \lambda_\text{IR} I  &-\mu I \\
\dot{R} =& \lambda_\text{IR} I & -\mu R. \label{eq:rdotsir}
\end{eqnarray}
In equation (\ref{eq:sdotSIR}) we assume that an infected individual will infect a susceptible instantly with a probability $\lambda_\text{SI}$, if they meet and the rate $SI$ is the rate of susceptibles and infected meeting one another. This requires that the population is well mixed. If the population is not well mixed, a probability of individuals from the different departments meeting each other would need to be introduced. 

\paragraph{Basic Reproduction Number}
Starting with those derivatives one defines the basic reproduction number $R_0=\lambda_\text{SI} / \lambda_\text{IR}$ assuming that the reproduction and death rate $\mu=0$ (following \citep{AND92}) by using the equations
\begin{eqnarray}
\dot{S} =& \ -\lambda_\text{SI} SI &  \label{eq:newsdotSIR}\\ 
\dot{I} =& \lambda_\text{SI} SI - \lambda_\text{IR} I  & \label{eq:newidotSIR}\\
\dot{R} =& \lambda_\text{IR} I \label{eq:newrdotSIR}&.
\end{eqnarray}
The trivial solution for a fixed point with the premise $\dot{S} = \dot{I} =\dot{R} = 0$ (The definition of a fix point is that there is no change) is that $I=0$. By writing equation (\ref{eq:newidotSIR}) like 
\begin{equation}
\dot{I} = (\lambda_\text{SI} S -\lambda_\text{IR}) I = \left( S-\frac{\lambda_\text{IR}}{\lambda_\text{SI}} \right) \lambda_\text{SI} I \label{eq:idotr0}
\end{equation}
one can see the number of infected will grow if $S > 1/R_0$ or fall if $S < 1/R_0$. $R_0$ could be interpreted as the number of susceptibles that get infected before an infected recovers. If one includes the death rate $\mu$, $R_0$ can be derived to be $R_0=\lambda_\text{SI} / (\lambda_\text{IR}+\mu)$.

\paragraph{Stable State}
Complex systems can exhibit all kinds of different interesting behaviors. Natural systems, which are still existent, need to be relatively stable because otherwise they would have been erased from earth. Mathematically speaking this means that they either have a stable fix point or a stable orbit around a fixed point. Fixed points can be found by inspecting the derivatives as it is described above. By observing equation equation (\ref{eq:idotr0}), it can easily be seen that by choosing $S^*=1/R_0$, $\dot{I}^*$ diminishes.
Plugging this into equations (\ref{eq:newsdotSIR}) and (\ref{eq:newrdotSIR}) shows that $I^*= 1/\lambda_\text{IR}$ leads to $\dot{S}^*=\dot{R}^* =0$.
In a system with demography ($\mu \neq 0$) one would derive
\begin{eqnarray}
S^* =& \frac{1}{R_0}& \\ 
I^* =& \frac{\mu}{\lambda_\text{SI}}&(1-R_0) \\
R^* =& 1-&\frac{1}{R_0}-\frac{\mu}{\lambda_\text{SI}}(R_0 -1).
\end{eqnarray}
Plugging them into the Jacobi matrix of the system leads to the eigenvalues, which define the oscillatory behavior of the system. Using this one can derive the frequency or respectively the period with which the system is oscillating. The interested reader is referred to \citep{matt2008modeling}. 
